\documentclass{article}
\usepackage[utf8]{inputenc}

\title{Sponsorship Report}
\author{Muhammed Sezer / Şevval Belkıs Dikkaya}
\date{\today}

\begin{document}

\maketitle

\section{Introduction}

In this report, we will detail our sponsorship agreement with NURUS, including the terms of the agreement, the benefits we received, and the results of our collaboration.

\section{Background}

Our university team was tasked with designing and building a fixed-wing aircraft for Teknofest. In order to create a high-quality UAV, we needed access to specialized equipment and materials. We reached out to NURUS, an innovative and R\&D-oriented company that produces office furniture, as well as works in the fields of aviation and technology, to explore the possibility of sponsorship.

After contacting Renan Gökyay, a representative of NURUS, we were able to secure a sponsorship package that included a budget of 20.000TL and access to their workspace and equipment. We used a variety of top-quality materials, including fabric, carbon, epoxy, and other composites, to build our fixed-wing aircraft.

\section{Sponsorship Agreement}

The sponsorship agreement began in December 2022 and will end in April 2023. As part of the agreement, NURUS required us to place their logos on the aircraft and team t-shirt, and to create a video in their factory.

\section{Benefits}

Through our collaboration with NURUS, we were able to benefit from their expertise and resources, including their workspace and equipment. We also received financial support.
Thanks to NURUS' sponsorship, we had access to a wealth of opportunities within their factory, which allowed us to create a superior aircraft compared to our competitors.

\section{Results}

As a result of our partnership with NURUS, we were able to create an exceptional aircraft that outperformed our competitors. We were also able to fulfill the requirements of the sponsorship agreement by placing NURUS' logos on our aircraft and t-shirt, and by creating a video in their factory.

\section{Factory Experience}

During our time at NURUS, we had access to their workspace and equipment, which allowed us to work on our aircraft in a professional setting. We were also able to collaborate with their team members who provided us with valuable insights and guidance on how to improve our aircraft.

Here are some of the steps we took during the process:

\begin{itemize}
    \item We used NURUS' specialized software to design and test our aircraft.
    \item We used their top-quality materials, including fabric, carbon, epoxy, and other composites, to build our aircraft.
    \item We used their tools and equipment to manufacture and assemble the aircraft, including a CNC machine, a laser cutter, and a 3D printer.
    \item We worked closely with their team members to troubleshoot any issues and optimize our design.  
	\item Access to NURUS' network of industry professionals and potential collaborators
	\item Exposure to new technologies and manufacturing processes, including additive manufacturing and composites fabrication
	\item Training sessions and workshops on topics such as design software, machining, and testing techniques
	\item Feedback and guidance from NURUS' experienced engineers and designers
	\item Opportunities to showcase your work and promote your team through NURUS' social media and marketing channels
	\item Invitations to attend industry events and conferences as representatives of NURUS and your university
	\item Potential for ongoing collaboration with NURUS on future projects or research initiatives
\end{itemize}

Here are some photos of the work we did at NURUS:



\section{Conclusion}

Our sponsorship agreement with NURUS was a success, and we are grateful for the support and resources they provided us. We look forward to the possibility of future collaborations with NURUS.

\end{document}
